Grove: A Bidirectionally Typed Collaborative Structure Editor Calculus

### 2024-10-25 figures/figure-disconnect.tex
Updates from Overleaf

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%% \figureDisconnect
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\newedge{DisconnectAlice}{R}
\newedge{DisconnectBob}{L}
\newcommand{\figureDisconnect}{
\begin{figure*}
%\hfill
\hskip0.12\columnwidth
%%%%%%%%
\begin{subfigure}[t]{0.21\textwidth}
\centering
\caption{
\begin{tikzpicture}[remember picture, overlay]
\path (-7.5em,0cm) node (node/Cycle/dx) [gray,anchor=base west] {{\textbf{\small Fig.~\ref*{fig:Cycle:d}}}};
%%%%
\path (0cm,0cm) node (node/Disconnect/a) [anchor=base] {\strut};
\path [draw,->,alice step] (node/Cycle/dx) to[star] (-2em, 0cm |- node/Disconnect/a);
\end{tikzpicture}
}%
\label{fig:Disconnect:a}
\figureCode{\hole{} * \hole{} + \hole{} * \hole{}\otherVertexVskip\strut}%
\begin{tikzpicture}
\path (0cm,0cm) graph[graph style] {
 root[root style] -> {
  "\vWrapPlus" [> "\eWrapPlus"] -> {
   "\vSimpleTimes" [> "\eNestedPartsBob"'],
   "\vMultiCycleTimes" [> "\eMultiCycleAliceTimes"]
  }
 }
};
\end{tikzpicture}
\end{subfigure}
%%%%%%%%
\hfill
%%%%%%%%
\begin{subfigure}[t]{0.21\textwidth}
\centering
\caption{
\begin{tikzpicture}[remember picture, overlay]
\path (0cm,0cm) node (node/Disconnect/b) [anchor=base] {\strut};
\path [draw,->,alice step] (node/Disconnect/a) to[star] (-2em, 0cm |- node/Disconnect/b);
\end{tikzpicture}
}%
\label{fig:Disconnect:b}
\figureCode{\hole{} * \parens{\hole{} * \hole{}} + \hole{}\otherVertexVskip\strut}%
\begin{tikzpicture}
\path (0cm,0cm) graph[graph style] {
 root[root style] -> {
  "\vWrapPlus" [> "\eWrapPlus"] -> {
   "\vSimpleTimes" [> "\eNestedPartsBob"'] -> {
    {},
    "\vMultiCycleTimes" [> "\eDisconnectAlice", >alice edge]
   },
   {}
  }
 }
};
\end{tikzpicture}
\end{subfigure}
%%%%%%%%
\hfill
%%%%%%%%
\begin{subfigure}[t]{0.21\textwidth}
\centering
\caption{
\begin{tikzpicture}[remember picture, overlay]
\path (0cm,0cm) node (node/Disconnect/c) [anchor=base] {\strut};
\path [draw,->,bob step] (node/Disconnect/a) to[out=15,in=165,star] (-2em, 0cm |- node/Disconnect/c);
\end{tikzpicture}
}%
\label{fig:Disconnect:c}
\figureCode{\hole{} + \parens{\hole{} * \hole{}} * \hole{}\otherVertexVskip\strut}%
\begin{tikzpicture}
\path (0cm,0cm) graph[graph style] {
 root[root style] -> {
  "\vWrapPlus" [> "\eWrapPlus"] -> {
   {},
   "\vMultiCycleTimes" [> "\eMultiCycleAliceTimes"] -> {
    "\vSimpleTimes" [> "\eDisconnectBob"', >bob edge],
    {}
   }
  }
 }
};
\end{tikzpicture}
\end{subfigure}
%%%%%%%%
\hfill
%%%%%%%%
\begin{subfigure}[t]{0.21\textwidth}
\centering
\caption{
\begin{tikzpicture}[remember picture, overlay]
\path (0cm,0cm) node (node/Disconnect/d) [anchor=base] {\strut};
\path [draw,->,merge step] (node/Disconnect/b) to[out=15,in=165] (-2em, 0cm |- node/Disconnect/d);
\path [draw,->,merge step] (node/Disconnect/c) to (-2em, 0cm |- node/Disconnect/d);
\end{tikzpicture}
}%
\label{fig:Disconnect:d}
\figureCode{\hole{} + \hole{}\otherVertexVskip\cycleVertex{2} = \hole{} * \parens{\cycleVertex{2} * \hole{}}}%
\begin{tikzpicture}
\path (0cm,0cm) graph[graph style] {
 root[root style] -> {
  "\vWrapPlus" [> "\eWrapPlus"]
 }
};
\path (-0.5cm,-2cm) graph[graph style] { plus/"\vSimpleTimes" };
\path ( 0.5cm,-2cm) graph[graph style] { times/"\vMultiCycleTimes" };
\path[draw,->,merge edge] (times) to ["\eMultiCycleBobTimes"'anchor=north,out=-135,in=-45] (plus);
\path[draw,->,merge edge] (plus) to ["\eMultiCycleBobPlus"anchor=south,out=45,in=135] (times);
\end{tikzpicture}
\end{subfigure}
%%%%%%%%
\hfill{}
\caption{Example of Disconnection.}%
\label{fig:Disconnection}
\end{figure*}
}

>>>>

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%% \figureDisconnect
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\newedge{DisconnectAlice}{R}
\newedge{DisconnectBob}{L}
\newcommand{\figureDisconnect}{
\begin{figure*}
\hfill
% \hskip0.1\columnwidth
%%%%%%%%
\begin{subfigure}[t]{0.20\textwidth}
\centering
\caption{
\begin{tikzpicture}[remember picture, overlay]
% \path (-7.5em,0cm) node (node/Cycle/dx) [gray,anchor=base west] {{\textbf{\small Fig.~\ref*{fig:Cycle:d}}}};
%%%%
\path (0cm,0cm) node (node/Disconnect/a) [anchor=base] {\strut};
% \path [draw,->,alice step] (node/Cycle/dx) to[star] (-2em, 0cm |- node/Disconnect/a);
\end{tikzpicture}
}%
\label{fig:Disconnect:a}
\figureCode{\hole{} * \hole{} + \hole{} * \hole{}\otherVertexVskip\strut}%
\begin{tikzpicture}
\path (0cm,0cm) graph[graph style] {
 root[root style] -> {
  "\vWrapPlus" [> "\eWrapPlus"] -> {
   "\vSimpleTimes" [> "\eNestedPartsBob"'],
   "\vMultiCycleTimes" [> "\eMultiCycleAliceTimes"]
  }
 }
};
\end{tikzpicture}
\end{subfigure}
%%%%%%%%
\hfill
%%%%%%%%
\begin{subfigure}[t]{0.22\textwidth}
\centering
\caption{
\begin{tikzpicture}[remember picture, overlay]
\path (0cm,0cm) node (node/Disconnect/b) [anchor=base] {\strut};
\path [draw,->,alice step] (node/Disconnect/a) to[star] (-2em, 0cm |- node/Disconnect/b);
\end{tikzpicture}
}%
\label{fig:Disconnect:b}
\figureCode{\hole{} * \parens{\hole{} * \hole{}} + \hole{}\otherVertexVskip\strut}%
\begin{tikzpicture}
\path (0cm,0cm) graph[graph style] {
 root[root style] -> {
  "\vWrapPlus" [> "\eWrapPlus"] -> {
   "\vSimpleTimes" [> "\eNestedPartsBob"'] -> {
    {},
    "\vMultiCycleTimes" [> "\eDisconnectAlice", >alice edge]
   },
   {}
  }
 }
};
\end{tikzpicture}
\end{subfigure}
%%%%%%%%
\hfill
%%%%%%%%
\begin{subfigure}[t]{0.22\textwidth}
\centering
\caption{
\begin{tikzpicture}[remember picture, overlay]
\path (0cm,0cm) node (node/Disconnect/c) [anchor=base] {\strut};
\path [draw,->,bob step] (node/Disconnect/a) to[out=15,in=165,star] (-2em, 0cm |- node/Disconnect/c);
\end{tikzpicture}
}%
\label{fig:Disconnect:c}
\figureCode{\hole{} + \parens{\hole{} * \hole{}} * \hole{}\otherVertexVskip\strut}%
\begin{tikzpicture}
\path (0cm,0cm) graph[graph style] {
 root[root style] -> {
  "\vWrapPlus" [> "\eWrapPlus"] -> {
   {},
   "\vMultiCycleTimes" [> "\eMultiCycleAliceTimes"] -> {
    "\vSimpleTimes" [> "\eDisconnectBob"', >bob edge],
    {}
   }
  }
 }
};
\end{tikzpicture}
\end{subfigure}
%%%%%%%%
\hfill
%%%%%%%%
\begin{subfigure}[t]{0.24\textwidth}
\centering
\caption{
\begin{tikzpicture}[remember picture, overlay]
\path (0cm,0cm) node (node/Disconnect/d) [anchor=base] {\strut};
\path [draw,->,merge step] (node/Disconnect/b) to[out=15,in=165] (-2em, 0cm |- node/Disconnect/d);
\path [draw,->,merge step] (node/Disconnect/c) to (-2em, 0cm |- node/Disconnect/d);
\end{tikzpicture}
}%
\label{fig:Disconnect:d}
\figureCode{\hole{} + \hole{}\otherVertexVskip\cycleVertex{2} = \hole{} * \parens{\cycleVertex{2} * \hole{}}}%
\begin{tikzpicture}
\path (0cm,0cm) graph[graph style] {
 root[root style] -> {
  "\vWrapPlus" [> "\eWrapPlus"]
 }
};
\path (-0.5cm,-2cm) graph[graph style] { plus/"\vSimpleTimes" };
\path ( 0.5cm,-2cm) graph[graph style] { times/"\vMultiCycleTimes" };
\path[draw,->,merge edge] (times) to ["\eMultiCycleBobTimes"'anchor=north,out=-135,in=-45] (plus);
\path[draw,->,merge edge] (plus) to ["\eMultiCycleBobPlus"anchor=south,out=45,in=135] (times);
\end{tikzpicture}
\end{subfigure}
%%%%%%%%
\hfill{}
\caption{(a) We start with a tree containing \vSimpleTimes{} and \vMultiCycleTimes{}. (b) Alice relocates \vMultiCycleTimes{} to a child position of \vSimpleTimes{}. (c) Bob relocates \vSimpleTimes{} to a child position of \vMultiCycleTimes{}. (d) When merged, the resulting cycle becomes disconnected from the rest of the graph, forming a \emph{unicycle}. During decomposition, we break unicycles by leaving a \emph{unicycle conflict reference} at an arbitrarily chosen edge.}%
\Description{This figure shows an example of a disconnected component}
\label{fig:Disconnection}
\end{figure*}
}

### 2024-10-25 figures/figure-multi-parent.tex
Updates from Overleaf

%\hfill
\hskip0.12\columnwidth

@@

@@

\path (-7.5em,0cm) node (node/MultiChild/cx) [gray,anchor=base west] {{\textbf{\small Fig.~\ref*{fig:MultiChild:c}}}};

@@

\path [draw,->,alice step] (node/MultiChild/cx) to[star] (-2em, 0cm |- node/MultiParent/a);

@@

\figureCode{w * \hole{} + \hole{}\otherVertexVskip\phantom{\multiVertex{18} = w}}%

@@

\figureCode{\hole{} * w + \hole{}\otherVertexVskip\phantom{\multiVertex{18} = w}}%

@@

\figureCode{\hole{} * \hole{} + w\otherVertexVskip\phantom{\multiVertex{18} = w}}%

@@

@@

\figureCode{\hole{} * \multiVertex{18} + \multiVertex{18}\otherVertexVskip\multiVertex{18} = w}%

@@

@@

\caption{Example of Multi-Parent Conflicts.}%

>>>>

% \hskip0.1\columnwidth

@@

\begin{subfigure}[t]{0.12\linewidth}

@@

% \path (-7.5em,0cm) node (node/MultiChild/cx) [gray,anchor=base west] {{\textbf{\small Fig.~\ref*{fig:MultiChild:c}}}};

@@

% \path [draw,->,alice step] (node/MultiChild/cx) to[star] (-2em, 0cm |- node/MultiParent/a);

@@

\figureCode{w * \hole{} + \hole{}\otherVertexVskip\phantom{\multiVertex{58} = w}}%

@@

\figureCode{\hole{} * w + \hole{}\otherVertexVskip\phantom{\multiVertex{58} = w}}%

@@

\figureCode{\hole{} * \hole{} + w\otherVertexVskip\phantom{\multiVertex{58} = w}}%

@@

\begin{subfigure}[t]{0.18\linewidth}

@@

\figureCode{\hole{} * \multiVertex{58} + \multiVertex{58}\otherVertexVskip\multiVertex{58} = w}%

@@

\begin{subfigure}[t]{0.13\linewidth}

@@

\caption{(a) We start in a state with a variable, \li{w}, and two holes. (b) Alice relocates \li{w} to the left hole. (c) Bob relocates \li{w} to the right hole. (d) After merging, vertex \vNestedPartsAlice{} has two incoming edges, i.e. it has a \emph{relocation conflict}. The corresponding decomposition leaves a \emph{relocation conflict reference} at both locations, partially addressing the \textbf{relocation conflict problem}. Terms that have a relocation conflict are tracked separately by decomposition. (e) The relocation conflict can be resolved by deleting all but one reference.}%
\Description{This figure depicts an example of relocation conflicts}
